---
title: "coding_exercise"
author: "Dario Galindo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
source("set_up.R")

```

```{r}
bison <- data("knz_bison")

```

```{r}
("knz_bison")
```

Create a new column in the bison dataset that calculates the individual’s age at the time of observation.

```{r}
mutate(knz_bison, age= rec_year-animal_yob )
```


```{r}
?mutate()

  
```


Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}

filter(knz_bison, animal_weight > mean(animal_weight, na.rm = TRUE))
```



Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}

knz_bison%>%
  ggplot(aes(x=animal_sex, y= animal_weight))+
  geom_boxplot()

```


```{r}
knz_bison%>%
  ggplot(aes(animal_weight, fill=animal_sex))+
  geom_histogram()
```

```{r}

knz_bison %>% 
  levene_test(animal_weight ~ animal_sex)
```

```{r}
knz_bison %>% 
  t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE) 
```
 TRYING ANOTHER PUSH
 
